Runtime-Assisted Convergence in Replicated Data Types

### 2021-11-20 implementation.tex
Implementation Fig added
Evaluation text in

@@

We implement \quark runtime as a lightweight shim layer on top of
Scylla -- an off-the-shelf distributed data store~\cite{scylla}. We
rely on Scylla for inter-replica communication, data replication,
persistence, and fault tolerance. \quark translates the high-level
mergeable data type implementations in OCaml to their low-level
representations in the backing store and organizes their well-formed
distributed executions. Fig.~\ref{fig:system} illustrates the overall
architecture.

>>>>

\begin{figure}[ht]
  \centering
    \includegraphics[scale=0.35]{Figures/implementation2}
\caption{\quark implementation architecture}
\label{fig:implementation}
\end{figure}

@@

We realize a prototype of \quark runtime as a lightweight shim layer
on top of Scylla -- an off-the-shelf distributed data
store~\cite{scylla}. We rely on Scylla for inter-replica
communication, data replication, persistence, and fault tolerance.
\quark translates the high-level mergeable data type implementations
in OCaml to their low-level representations in the backing store and
organizes their well-formed distributed executions.
Fig.~\ref{fig:implementation} illustrates the overall architecture.
